s.function

### 2025-01-23 src/s_la_per_firm_corrected.Rmd
lad curves

library(tidyverse)
library(broom)
library(rprojroot)
#library(rgdal)
library(sf)
library(modelr)
#library(survival)
#library(rgeos)
library(spdep)
library(tidygeocoder)
# library(geosphere)
# library(raster)
library(rms)
library(stargazer)
library(ggbump)

@@

ggplot(pred %>% 
              left_join(a.la), 
            aes(x = year, y = n, color = fast, group = ladcd)) +
  geom_line(aes(y = prednls), size = .1, alpha = .7) +
  scale_x_continuous(NULL, labels = as.character(df$year), breaks = df$year) +
  #geom_vline(xintercept = xmid.uk) +
  ylab("N. of websites / per firm") + 
  labs(color = "Website \ndiffusion speed") +
  theme(legend.position=c(.9,.15)) +
  scale_color_manual(values = c("fast" = "purple",
                                "slow"="orange"),
                     limits = force) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        panel.grid.minor = element_blank()) +
  geom_vline(xintercept = xmid.uk, colour="grey30", linetype="dashed")

>>>>

library(tidyverse)
library(broom)
library(rprojroot)
#library(rgdal)
library(sf)
library(modelr)
#library(survival)
#library(rgeos)
library(spdep)
library(tidygeocoder)
# library(geosphere)
# library(raster)
library(rms)
library(stargazer)
library(ggbump)
library(latex2exp)

@@

ggplot(pred %>% 
              left_join(a.la), 
            aes(x = year, y = n, color = fast, group = ladcd)) +
  geom_line(aes(y = prednls), size = .1, alpha = .7) +
  scale_x_continuous(NULL, labels = as.character(df$year), breaks = df$year) +
  #geom_vline(xintercept = xmid.uk) +
  ylab("N. of websites / per firm") + 
  labs(color = "Website diffusion speed") +
  theme(legend.position=c(.9,.15)) +
  scale_color_manual(values = c("fast" = "purple",
                                "slow"="orange"),
                     limits = force) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        panel.grid.minor = element_blank(),
        legend.position = "bottom") +
  geom_vline(aes(xintercept = xmid.uk, linetype="dashed"), colour="grey30") +
  scale_linetype_manual(values=c("dashed"), 
                        labels = c(""), 
                        name = unname(TeX(c("$t_{0}$ for the UK"))))
